Mysis analysis

### 2015-10-12 _drafts/mysisAnalysis.Rmd

---
title: "Mysis analysis"
author: "John Tipton"
date: "September 9, 2015"
output: html_document
---
This document shows the analyses performed in Johnson et. al. We start by loading packages and define helper functions

```{r loadLibraries, echo=TRUE, include=FALSE, message=FALSE}
options(digits=3)
set.seed(123)
require(knitr)
require(ggplot2)
require(Gmisc)
require(MASS)
require(stringr)
require(mgcv)
require(lme4)

@@

```{r countModelResults, echo=TRUE}
tableData <- cbind(summary(nbmod)$coeff[1:6, ])
colnames(tableData) <- c("Estimate", "Std. Error", "z value", "Pr(>|z|)")
rownames(tableData) <- c("Intercept", "Net Size", "August", "September", 
                         "Net Size * August", "Net Size * September")
kable(tableData, digits = 4, format="pandoc")
```

@@

```{r sexResults, echo=TRUE, cache=TRUE}
tableData <- cbind(summary(nbmod)$coeff)
colnames(tableData) <- c("Estimate", "Std. Error", "z value", "Pr(>|z|)")
rownames(tableData) <- c("Intercept", "Net Size", "Females", "Juveniles", 
                         "Unknown Gender", "August", "September", 
                         "Net Size * Females", "Net Size * Juveniles", 
                         "Net Size * Unknowns", "Net Size * August",
                         "Net Size * September",
                         "Females * August", "Juveniles * August", 
                         "Unknown Gender * August",
                         "Females * September", "Juveniles * September", 
                         "Unknown Gender * September")
kable(tableData, digits = 4, format="pandoc")
```

@@

On this reduced model, the results shown below show that there is no evidence of an effect on the number of counts observed between the two net sizes (p=`r I(round(summary(nbmod)$coef[2, 4], 4))`).
```{r sexResultsReduced, echo=TRUE, cache=TRUE}
tableData <- cbind(summary(nbmod)$coeff)
colnames(tableData) <- c("Estimate", "Std. Error", "z value", "Pr(>|z|)")
rownames(tableData) <- c("Intercept", "Net Size", "Females", "Juveniles", 
                         "Unknown Gender", "August", "September", 
                         "Net Size * Females", "Net Size * Juveniles", 
                         "Net Size * Unknowns", 
                         "Females * August", "Juveniles * August", 
                         "Unknown Gender * August",
                         "Females * September", "Juveniles * September", 
                         "Unknown Gender * September")
kable(tableData, digits = 4, format="pandoc")
```

@@

```{r juvenileResults, echo=TRUE, cache=TRUE}
tableData <- cbind(summary(brmod)$coeff$mean)
colnames(tableData) <- c("Estimate", "Std. Error", "z value", "Pr(>|z|)")
rownames(tableData) <- c("Intercept", "Net Size", "August", "September", 
                         "Net Size * August", "Net Size * September")
kable(tableData, digits = 4, format="pandoc")
```

@@

kable(tableData, digits = 4, format="pandoc")
```

>>>>

title: "Mysis analysis"
author: "John Tipton"
date: "October 12, 2015"
---
This document shows the analyses performed in Johnson et. al. We start by loading packages and define helper functions

```{r loadLibraries, echo=TRUE, include=FALSE, message=FALSE}
options(digits=3)
set.seed(123)
require(knitr)
knitr::opts_chunk$set(fig.path='../images/mysisAnalysis-')
require(ggplot2)
require(Gmisc)
require(MASS)
require(stringr)
require(mgcv)
require(lme4)

@@

```{r countModelResults, echo=TRUE}
tableData <- cbind(summary(nbmod)$coeff[1:6, ])
colnames(tableData) <- c("Estimate", "Std. Error", "z value", "Pr(>|z|)")
rownames(tableData) <- c("Intercept", "Net Size", "August", "September", 
                         "Net Size * August", "Net Size * September")
kable(tableData, digits = 4, format="html")
```

@@

```{r sexResults, echo=TRUE, cache=TRUE}
tableData <- cbind(summary(nbmod)$coeff)
colnames(tableData) <- c("Estimate", "Std. Error", "z value", "Pr(>|z|)")
rownames(tableData) <- c("Intercept", "Net Size", "Females", "Juveniles", 
                         "Unknown Gender", "August", "September", 
                         "Net Size * Females", "Net Size * Juveniles", 
                         "Net Size * Unknowns", "Net Size * August",
                         "Net Size * September",
                         "Females * August", "Juveniles * August", 
                         "Unknown Gender * August",
                         "Females * September", "Juveniles * September", 
                         "Unknown Gender * September")
kable(tableData, digits = 4, format="html")
```

@@

On this reduced model, the results shown below show that there is no evidence of an effect on the number of counts observed between the two net sizes (p=`r I(round(summary(nbmod)$coef[2, 4], 4))`).
```{r sexResultsReduced, echo=TRUE, cache=TRUE}
tableData <- cbind(summary(nbmod)$coeff)
colnames(tableData) <- c("Estimate", "Std. Error", "z value", "Pr(>|z|)")
rownames(tableData) <- c("Intercept", "Net Size", "Females", "Juveniles", 
                         "Unknown Gender", "August", "September", 
                         "Net Size * Females", "Net Size * Juveniles", 
                         "Net Size * Unknowns", 
                         "Females * August", "Juveniles * August", 
                         "Unknown Gender * August",
                         "Females * September", "Juveniles * September", 
                         "Unknown Gender * September")
kable(tableData, digits = 4, format="html")
```

@@

```{r juvenileResults, echo=TRUE, cache=TRUE}
tableData <- cbind(summary(brmod)$coeff$mean)
colnames(tableData) <- c("Estimate", "Std. Error", "z value", "Pr(>|z|)")
rownames(tableData) <- c("Intercept", "Net Size", "August", "September", 
                         "Net Size * August", "Net Size * September")
kable(tableData, digits = 4, format="html")
```

@@

kable(tableData, digits = 4, format="html")
```
